Title here

### 2016-09-14 portfolio/text/ms.Rmd
Strip whitespace; add model checking note
Copy editing

We obtained landings and revenue data for 
all permit holders in Alaska 
from `r range_yrs[1]` to `r range_yrs[2]`
from the Alaskan Commercial Fisheries Entry Commission (CFEC).
These data represent a total of 
nearly `r round(ndat$initial_tot_rev/1e9)` billion 2009 USD
and a combined `r round(ndat$initial/1e6,1)` million rows of data.
We adjusted for inflation by setting all revenues in 2009 USD 
based on data from TODO.
We implemented a number of filtering steps 
to focus on individuals actively engaged in commercial fishing
(Supporting Information). 
In particular, we removed permit holders whose median revenue
was less than $10,000 2009 USD.

Our models focused on the predictor species diversity, 
while controlling for effort. 
We calculated effective species diversity for
permit holder $i$ and year $t$ as the inverse of 
Simpson's diversity index $\lambda$ [@simpson1949]
weighted by revenue $R$ ('species diversity'):

@@

The basic model is a hierarchical linear regression with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time (year) $t$:

@@

\begin{equation}
\label{eq:mean}
\widehat{\log(R_{i,t})} = \beta_{0,j,t} -
  \beta_{1,j} S_{i,t} I_{i,t} +
  \beta_{2,j} S_{i,t} I_{i,t} +
  \beta_3 D_{i,t} -
  \beta_4 S_{i,t} D_{i,t} I_{i,t} +
  \beta_5 S_{i,t} D_{i,t} I_{i,t} +
  \log(R_{i,t-1})
\end{equation}

@@

\begin{align}
\beta_{1,j} &\sim \mathrm{N} \left(\beta_1, \sigma^2_{\beta_1}\right),\\
\beta_{2,j} &\sim \mathrm{N} \left(\beta_1, \sigma^2_{\beta_2}\right).
\end{align}

@@

We fit our models with Stan 2.11.1
[@hoffman2014; @standevelopmentteam2015; @standevelopmentteam2015a; @carpenter2015]
and R 3.3.1 [@rcoreteam2016].
Stan implements the 
No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm [@hoffman2014]
to perform Bayesian statistical inference.
We ran four chains and 2,000 iterations and discarded
the first 1,000 iterations of each chain
as warm up (i.e. 4,000 final samples). 
We checked for chain convergence visually with trace plots.
We also ensured that $\hat{R}<1.05$ (the potential scale reduction factor)
and that the effective sample size was 
greater than 200 for all parameters [@gelman2014].
Code to reproduce our results (with a simulated data set)
is available at <https://github.com/NCEAS/pfx-commercial>.

@@

Fishing can be big $ but is risky, for example, Alaska

What's been done

>>>>

We obtained fisheries landings and revenue data for
all permit holders in Alaska
from `r range_yrs[1]` to `r range_yrs[2]`
from the Alaskan Commercial Fisheries Entry Commission (CFEC).
These data represent a total of
nearly `r round(ndat$initial_tot_rev/1e9)` billion 2009 USD
and a combined `r round(ndat$initial/1e6,1)` million rows of data.
We adjusted for inflation by setting all revenues in 2009 USD
based on data from TODO.
We implemented a number of filtering steps
to focus on individuals actively engaged in commercial fishing
(Supporting Information).
In particular, we removed permit holders whose median revenue
was less than $10,000 2009 USD.

Our models focused on the predictor species diversity,
while controlling for effort.
We calculated effective species diversity for
permit holder $i$ and time (year) $t$ as the inverse of
Simpson's diversity index $\lambda$ [@simpson1949]
weighted by revenue $R$ ('species diversity'):

@@

The basic model is a hierarchical linear regression with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time $t$:

@@

\begin{equation}
\label{eq:mean}
\widehat{\log(R_{i,t})} = \beta_{0,j,t} -
  \beta_{1,j} S_{i,t} I_{i,t} +
  \beta_{2,j} S_{i,t} I_{i,t} +
  \beta_3 D_{i,t} -
  \beta_4 S_{i,t} D_{i,t} I_{i,t} +
  \beta_5 S_{i,t} D_{i,t} I_{i,t} +
  \log(R_{i,t-1}),
\end{equation}

@@

\begin{align}
\beta_{1,j} &\sim \mathrm{N} \left(\beta_1, \sigma^2_{\beta_1}\right),\\
\beta_{2,j} &\sim \mathrm{N} \left(\beta_2, \sigma^2_{\beta_2}\right).
\end{align}

@@

We fit our models with Stan 2.11.1
[@hoffman2014; @standevelopmentteam2015; @standevelopmentteam2015a; @carpenter2015]
and R 3.3.1 [@rcoreteam2016].
Stan implements the
No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm [@hoffman2014]
to perform Bayesian statistical inference.
We ran four chains and 2,000 iterations and discarded
the first 1,000 iterations of each chain
as warm up (i.e. 4,000 final samples).
We checked for chain convergence visually with trace plots.
We also ensured that $\hat{R}<1.05$ (the potential scale reduction factor)
and that the effective sample size was
greater than 200 for all parameters [@gelman2014].
We verified that our model was coded correctly by
comparing our estimates to an ad-hoc two-stage
model fit with the lme4 R package [@bates2015],
and by fitting our model to simulated data
and recovering the true values.
Code to reproduce our results (with a simulated data set)
is available at <https://github.com/NCEAS/pfx-commercial>.

@@
